Modal Abstractions for Virtualizing Memory Addresses

### 2025-08-17 examples.tex
okay apparently I missed one use of \del

\del{
A PTE points-to, as we already brifly mentioned, is defined just like the normal virtual points-to of Figure \ref{fig:virtualpointstosharing}, except the physical address (here, \textsf{pa}) is explicit in the assertion 
rather than existentially quantified:\\
\centerline{$
    \vaddr\mapsto_{\textsf{vpte,q}} \; \paddr \; \vpage : \mathsf{vProp}~\Sigma \stackrel{\triangle}{=} 
    \exists \delta\ldotp
	(\lambda \mathit{cr3val}\ldotp
	\ghostmaptoken{\delta{}s}{\mathit{cr3val}}{\delta}) \ast 
  \fracghostmaptoken{\delta}{\vaddr}{\paddr}{\qfrac} \ast \paddr \mapsto_{\mathsf{p}} \vpage
$}\\
This supports rules for accessing memory
at that virtual address, but exposing the physical location being modified
makes this convenient to use for page table modifications, since we must ensure
the modified data is at the specific physical location that will be used as the L1 entry.
}
% After obtaining a virtual address \textsf{pte\_addr} in \textsf{rax} backed 
% by the physical memory for the L1 entry that will be used to translate the virtual addresses
% we are mapping, we save it to \textsf{r14} to be updated later in Line 9.

>>>>

% After obtaining a virtual address \textsf{pte\_addr} in \textsf{rax} backed 
% by the physical memory for the L1 entry that will be used to translate the virtual addresses
% we are mapping, we save it to \textsf{r14} to be updated later in Line 9.
